Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex
continuing ...

To evaluate our approach, we compare the cost of diagnosing
a collection of faulty versions using \sfl{}
against \comb{}.

@@

Recall from Section~\ref{sec:approach} that the \comb{} combination
takes on input a value denoting the $k$ most suspicious distinct
files. To evaluate the effectiveness of \comb{}, we compared its
performance with \sfl{} for each defect on each subject program from
the dataset, for $k\in\{5,10\}$. These files are obtained directly
from the ranking. We refer to these variations as \combpar{k}. We
compared \combpar{5} and \combpar{10} against \sfl{} using the
following metrics.\Mar{Sofia, I don't see a reason for an equation to
  only show the difference of cost. Please describe precisely the
  metrics. In this case, I can't find what C stands for. Also,
 you need to describe precisely what top@n (or someother name) means
 in this context. Check if it makes sense for SFL.$\rightarrow$}

@@

where C is the cost of diagnosis. \Sof{@todo: Explain this better in section 2 or 3}
A positive $\Delta$C means that the faulty statement has risen in
the ranking reported by \sfl{} techniques when \ds{} is used,
producing a reduced cost of diagnosing.

%% Firstly, we ran the dataset presented in Section~\ref{sec:analysis}
%% with \sfl{} to gather the coverage statements ordered from the highest
%% faulty statement to the lowest faulty statement. This list is the
%% input of the \comb{} technique. For each defect, the list is evaluated
%% in order to get the top-$k$, for $k\in\{5,10\}$, of suspicious source
%% files. Then, Lithium minimizes each source file for each testcase of
%% the defect considering the top-$5$ (\comb{}-$5$) and top-$10$
%% (\comb{}-$10$) of source files separately. Some defects have more than
%% one testcase. In the end, we update spectra $S$ based on the output of
%% the minimization as presented in Figure~\ref{fig:ds-reduction} to
%% obtain the faulty statements ranking after minimization. All scripts
%% used to run these experiments and gather data are available at
%% \url{TBA} and \url{TBA}, respectively.

%% \Sof{Parei Aqui}

>>>>

To evaluate our approach, we compare the cost of diagnosing
a collection of faulty versions using \sfl{} versus \comb{}.

@@

Recall from Section~\ref{sec:approach} that the \comb{}
takes as input a value $k$ that denotes the $k$ most suspicious distinct
classes to be considered. To evaluate the effectiveness of \comb{}, following
related work, we compared its
performance with \sfl{} for each defect on each subject program from
the dataset, for $k\in\{5,10\}$. These classes are obtained directly
from the ranking. We refer to these variations as \combpar{k}. We
compared \combpar{5} and \combpar{10} against \sfl{} using the
following metrics.\Mar{Sofia, I don't see a reason for an equation to
  only show the difference of cost. Please describe precisely the
  metrics. In this case, I can't find what C stands for. Also,
 you need to describe precisely what top@n (or someother name) means
 in this context. Check if it makes sense for SFL.$\rightarrow$}\Rui{It might
 be good to keep it just to give it some emphasis... }

@@

\noindent
where $C$ is the cost of diagnosis. \Rui{At this point, you need to explain what
the cost of diagnosis is: C is the number of statemetns (?) that need to be
inspected before finding the fault, right? We also need to say that we assume a
perfect bug understanding: that is, when the developer sees the bug in the
ranking, he can say that it is the faulty one.}
A positive $\Delta$C means that the position of the faulty statement has decreased
in the ranking reported computed by \combpar{k}. Hence, reducing the cost to
find the bug.
